CF Registry Analysis - ROC

### 2024-09-19 Christine Chan/CF Registry/cf_registry_ROC_analysis.qmd
Update cf_registry_ROC_analysis.qmd

@@

>>>>

## Boxplot

@@

## Dotplot

```{r}
ggplot(roc_df, aes(x = `OGTT 2-hour`, y = hgba1c)) +
  geom_jitter(alpha = 0.25) +
  ylab("HbA1c") +
  theme_classic(base_size = 20)
```

## Violin plot

```{r}
ggplot(roc_df, aes(x = `OGTT 2-hour`, y = hgba1c)) +
  geom_violin(aes(fill = `OGTT 2-hour`)) +
  ylab("HbA1c") +
  theme_classic(base_size = 20) +
  theme(legend.position = "none")
```
